---
title: "Exploratory Template"
author: "Willie McRae"
date: "2016"
output: 
  html_document: 
    toc: yes
---
The goals are;

1. To deeply understand a single data file 
2. Surface high level relationships between variables   
3. Prepare thoughts and approaches for pre-processing and modeling 

```{r setup, include = FALSE}
# Find TODO Ctrl+Shift+F, search for regex ^\s*# TODO

# Set Working Directory

# Install and load packages
install.packages("tidyverse", repos="http://cran.rstudio.com/")
library(tidyverse)


install.packages("GGally", repos="http://cran.rstudio.com/")
library(GGally)

# Plot theme
theme_a <- theme(panel.background = element_blank(),
                 legend.background = element_blank(),
                 legend.key = element_blank(),
                 panel.grid = element_blank(),
                 axis.text = element_text(colour = "black"),
                 axis.line.x = element_line(colour = "black", size = 0.5),
                 axis.line.y = element_line(colour = "black", size = 0.5))

```

This is an analysis of the () data set from (). 

The purpose of the investigation is to...  

```{r load, include = FALSE}
# Load data

```

# Raw - First Explore
What is the structure and characteristics of the data in raw form?  

I like to visualise this.  

```{r raw_explore_1}
# A meta-view of the data, views of classifications of variables etc

data_raw <- x # replace x with name of data frame to be analysed

### Class and NA
names <- names(data_raw)
class <- unlist(lapply(data_raw, class))
percent_na <- round(sapply(data_raw, function(x)  sum(is.na(x)) / length(x)), digits = 3)
data_raw <- data.frame(names) # Create data frame to show the meta-data
data_raw$class <- as.factor(class)
data_raw$percent_na <- percent_na 

class(data_raw$class)

### Visual of the raw data by class and % NA
ggplot(data = data_raw, aes(x = names, fill = percent_na)) +
  geom_bar() +
  coord_flip() +
  theme_a +
  labs(title = "Raw data by class and % NA", x = "Variable") +
  facet_wrap(~ class, nrow = 1)

```

# Raw - Second Explore 
What are the relationships between variables in raw form?  

```{r raw_explore_2}
# Look at summary statistics and quick exploratory visuals

# Create a correlation matrix

ggcorr(d, method = c("pairwise", "pearson"), nbreaks = 5, hjust = 0.75, layout.exp = 2) +
  labs(title = "Correlation matrix of raw data")

# Use GGally

```

# Clean
What transformations of variables will improve the data?
```{r clean}
# Names (consistent)

# Classes (Date, Number, Character, Factor)

num_vars <- c("")
d[c(num_vars)] <- lapply(d[c(num_vars)], as.factor)

date_vars <- c("")
d[c(date_vars)] <- lapply(d[c(date_vars)], as.Date, format = "%d/%m/%Y") #Check format!!

factor_vars <- c("")
d[c(factor_vars)] <- lapply(d[c(factor_vars)], as.factor)

```

# Tidy
What transformations of structure will improve the data?
```{r tidy}
# Prepare data for visual exploration and summaries, using principles of tidy data; 
# Each row is an observation, each column is a variable

```


# Transformed - First Explore
What is the structure and characteristics of the data in transformed form? 
```{r transformed_explore_1}
# Refreshed meta-view of the data, views of classifications of variables etc

data_clean <- x # replace x with name of data frame to be analysed (the cleaned data frame)

### Class and NA
names <- names(data_clean)
class <- unlist(lapply(data_clean, class))
percent_na <- round(sapply(data_clean, function(x)  sum(is.na(x)) / length(x)), digits = 3)
data_clean <- data.frame(names) # Create data frame to show the meta-data
data_clean$class <- as.factor(class)
data_clean$percent_na <- percent_na 

class(data_clean$class)

### Visual of the raw data by class and % NA
ggplot(data = data_raw, aes(x = names, fill = percent_na)) +
  geom_bar() +
  coord_flip() +
  theme_a +
  labs(title = "Clean data by class and % NA", x = "Variable") +
  facet_wrap(~ class, nrow = 1)


```


# Transformed - Second Explore
What are the relationships between variables in raw form?
```{r transformed_explore_2}
# How do things look now the data has been manipulated?

```


# Visualize
Plots to highlight or uncover relationships.  
```{r visualize}
# Create plots

```


# Observations and recommendations
Thoughts on pre-processing, possible joins to other data sets, modeling approaches etc.  
```{r observations}
# What next?


```

