---
title: "Exploratory Template"
author: "Willie McRae"
date: "2016"
output: 
  html_document: 
    toc: yes
---
The goals are;

1. To deeply understand a single data file 
2. Surface high level relationships between variables   
3. Prepare thoughts and approaches for pre-processing and modeling 

```{r setup, include = FALSE}
# Set Working Directory

# Install and load packages
install.packages("tidyverse", repos="http://cran.rstudio.com/")
library(tidyverse)

```

This is an analysis of the () data set from (). 

The purpose of the investigation is to...  

```{r load, include = FALSE}
# Load data

```

# Raw - First Explore
What is the structure and characteristics of the data in raw form?  

```{r raw_explore_1}
# A meta-view of the data, views of classifications of variables etc

```

# Raw - Second Explore 
What are the relationships between variables in raw form?  

```{r raw_explore_2}
# Look at summary statistics and quick exploratory visuals

```

# Clean
What transformations of variables will improve the data?
```{r clean}
# Names (consistent)

# Classes (Date, Number, Character, Factor)


```

# Tidy
What transformations of structure will improve the data?
```{r tidy}
# Prepare data for visual exploration and summaries, using principles of tidy data; 
# Each row is an observation, each column is a variable

```


# Transformed - First Explore
What is the structure and characteristics of the data in transformed form? 
```{r transformed_explore_1}
# Refreshed meta-view of the data, views of classifications of variables etc

```


# Transformed - Second Explore
What are the relationships between variables in raw form?
```{r transformed_explore_2}
# How do things look now the data has been manipulated?

```


# Visualize
Plots to highlight or uncover relationships.  
```{r visualize}
# Create plots

```


# Observations and recommendations
Thoughts on pre-processing, possible joins to other data sets, modeling approaches etc.  
```{r observations}
# What next?


```

